---
title: "drug methylome"
author: "Shicheng Guo"
date: "July 7, 2016"
output: html_document
---
## Background

Sometime, you have different recombination to do the DMR calling. However, CHAMP only handle one csv samplesheet one time. Two way can solove this problem. first, change the code of the CHAMP or creat csv each time and do the DMR then rm the csv then do the next one. Here, I use the second way to do the DMR calling one by one with ESCA 450K methylation array dataset. 

* prepared a function DMR.CHAMP to do the DMR calling with one csv
* creat csv with default samplesheet (remove header) and then do the DMR

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r function, echo=TRUE}
DMR.CHAMP<-function(){
library("ChAMP")
setwd("/home/shg047/bak/zh/data/zhu2016/dataset/idat")
samplesheetFile=list.files(pattern="*csv")
sampleID=unlist(strsplit(samplesheetFile,"[.]"))[1]
# be sure to remove header of the samplesheet
sampleinfo<-read.table(samplesheetFile,head=T,sep="\t",as.is=T)
sampleinfo
system("mkdir resultsChamp")
# champ.process(fromIDAT = TRUE, fromFile = FALSE, directory = getwd(), resultsDir =paste(getwd(), "resultsChamp", sep = "/"), methValue = "B", filterDetP = TRUE,
#              detPcut = 0.01, filterXY = TRUE, removeDetP = 0, filterBeads = TRUE, beadCutoff =
#                0.05, filterNoCG = FALSE, QCimages = TRUE, batchCorrect = FALSE, runSVD =
#                TRUE, studyInfo = FALSE, infoFactor = c(), norm = "BMIQ", adjust.method = "BH",
#              adjPVal = 0.05, runDMR = TRUE, runCNA = FALSE, plotBMIQ = FALSE, DMRpval = 0.05,
#              sampleCNA=FALSE,plotSample = TRUE,groupFreqPlots=TRUE,freqThreshold=0.3, bedFile
#              = TRUE, methProfile = TRUE, controlProfile = FALSE)
myLoad<-champ.load(directory = getwd(),filterBeads=TRUE,QCimages = F)
# champ.CNA(intensity = myLoad$intensity, pd = myLoad$pd, loadFile = FALSE, batchCorrect = TRUE,
#           file = "intensity.txt", resultsDir = paste(getwd(), "resultsChamp", sep = "/"),
#           sampleCNA=TRUE, plotSample=TRUE, filterXY = TRUE, groupFreqPlots=TRUE,freqThreshold=0.3,
#           control=TRUE,controlGroup="Control")
# turn off the plot if you run it on the server since of the problem of X11
myNorm<-champ.norm(beta = myLoad$beta, rgSet = myLoad$rgSet, pd = myLoad$pd, mset = myLoad$mset,sampleSheet = samplesheet, resultsDir = paste(getwd(), "resultsChamp",sep = "/"), methValue = "B", fromIDAT = TRUE, norm = "BMIQ", fromFile = FALSE, betaFile,filter = TRUE, filterXY = TRUE, QCimages = F, plotBMIQ = F)
# identify MVP and it would be used in DMR calling
mylimma=champ.MVP(beta.norm = myNorm$beta, pd = data.frame(myLoad$pd), adjPVal = 0.5, adjust.method = "BH",compare.group = c("R","S"), resultsDir = paste(getwd(), "resultsChamp", sep = "/"),bedFile = F)
# Do DMR calling and save it to result2
library("doParallel")
result2=champ.DMR(betaNorm=myNorm$beta,design=myLoad$pd$Sample_Group,maxGap=300,
          cutoff=0.2,minProbes=3,smooth=TRUE,smoothFunction=loessByCluster,
          useWeights=FALSE,permutations=NULL,B=1000,pickCutoff=FALSE,
          pickCutoffQ=0.99,nullMethod="bootstrap",verbose=TRUE,cores=5,arraytype="450K",
          method = "Bumphunter",resultsFile=mylimma,meanLassoRadius=375,minSigProbesLasso=3,minDmrSep=1000,
          minDmrSize=50,adjPvalProbe=0.05,adjPvalDmr=0.05,pData=myLoad$pd)
Fileout1<-paste(sampleID,"resultsChamp.tar.gz",sep=".")
Fileout2<-paste(sampleID,"result2.txt",sep=".")
system("tar czvf Fileout ./resultsChamp")
write.table(result2,file=Fileout2,col.names=NA,row.names=T,sep="\t",quote=F)
}
```

## Saminfo file prepare and then do DMR one by one.

```{r cars}
drug=read.table("case1.txt",head=T,row.names=1,fill=T,sep="\t")
saminfo=read.table("SampleSheet2016.csv",head=T,fill=T,sep=",",skip=7,as.is=T)
sam2=read.table("Saminfo2.txt",head=T,fill=T,sep="\t")
saminfonew=saminfo[match(sam2[,1],saminfo[,1]),]
saminfonew=data.frame(saminfonew,sam2)
R<-apply(drug,1,function(x) which(x=="R"))
S<-data.frame(apply(drug,1,function(x) which(x=="S")))

for(i in 1:ncol(R)){
Res<-match(colnames(drug)[c(R[1,i],R[2,i])],as.character(saminfonew[,ncol(saminfonew)]))
Sen<-match(colnames(drug)[c(S[1,i],S[2,i])],as.character(saminfonew[,ncol(saminfonew)]))
saminfonew[Res,3]<-"R"
saminfonew[Sen,3]<-"S"
ResSam<-saminfonew[Res,]
SenSam<-saminfonew[Sen,]
output=rbind(ResSam,SenSam)
output
outputFile<-paste(colnames(R)[i],"samplesheet.csv",sep=".")
write.table(output,file=outputFile,col.names=T,row.names=F,sep=",",quote=F)
DMR.CHAMP()
}

```

